This feels impossible to write; too many have contributed to the successes I've experienced in my career. 
To everyone who has helped in getting me to this point, you have my everlasting thanks. 
I could not have dreamed of the success I've experienced without the support my parents have selflessly given throughout my life. 
Being a first generation college student, the support you offered to Kaitlin and me allowed us to pursue our dreams. 
I feel forever grateful for the family that pushed me to chase my dreams, and offered a hand whenever I needed help.
To my very first friend, my sister: You've always had my back. I have looked up to you for my whole life, and now I've finally one-upped you, boom roasted.

I would not have made it through a PhD without the friends I've made here at the University of Florida. 
To my wonderful partner: Mikayla, you've been my biggest supporter in lab and in life. 
You are exceptional, and have helped me in more ways than I could possibly write down. 
I'm looking forward to the chapters to follow the ones I've written here. 
To Alec and Emma, Jonathan and Enzo, and all of our UF Chemistry friends, thank you for making graduate school bearable.
My fellow Roitberg lab members: One of my biggest regrets from this experience is not getting to know the people I was working with sooner. 
The past 3 years have been a highlight of my graduate experience, working in the lab with everyone who has helped me on my journey.
I'm grateful to have had the opportunity to work alongside such brilliant and supportive colleagues.

Likewise, I never would've made it to this point without the formative experiences of living in those small town Missouri-villes: Smithville and Kirksville. 
To my friends from Truman, all of whom I can't begin to mention, I think back fondly on our time in Kirksville and how much we've all grown since then. 
I want to especially thank Matt for the time we spent living together and taking what seemed like every course together in college, and for being such a great friend and colleague since we graduated.
From Smithville, I want to give thanks to Christian and Mitch.
Our continued friendship, despite being reduced to weekend trips or holiday visits, is the reason Kansas City still feels like home.

To the educators who helped me get to this point, I cannot thank you enough for the service you provide that paved the path I walked to writing this dissertation. 
Listing anyone feels like a disservice to all those who helped me in ways I couldn't recognize at the time, but I would like to specifically thank my high school chemistry teacher, Dr. Lori Mertz, for stoking my interest in the field that I've now dedicated a decade to exploring. 
I also must mention my advisor from my days at Truman State University, Dr. Bill Miller, who introduced me to the vast field of computational chemistry and kindly guided a complete novice in programming toward useful applications of the scientific method in computational environments.

Thank you to my committee for overseeing my progress as a scientist throughout my doctorate.
I would like to especially thank Dr. Alberto Perez for being a consistently helpful educator and mentor, from teaching me the basics of chemical bonding in office hours to casual conversations at department events.
I also give my thanks to the University of Florida and the Department of Chemistry for providing me with the opportunity to study in this field I love, and for the computing resources on HiPerGator that have carried the weight of producing the results I discuss in this dissertation.
To anyone reading this document, I thank you for your attention and care to the work I've done over the course of my PhD.

Finally, but certainly not least, to my advisor and mentor, Adrian: Thank you for your guidance, patience, and all forms of support throughout this journey.
Your insight and expertise have pushed me to grow as a scientist, and constantly renew my desire to understand the world we live in a bit more deeply. 
Beyond being a supportive supervisor, I cannot thank you enough for the humanity you bring to our work environment. 
Having a knowledgeable boss is great for a developing scientist, but what has truly made my time here special and memorable is the understanding and care that you bring to every interaction. 
